### 2021-07-09 doc/thesis/chapters/dsp.tex
text update
\includepicture function with floating option; new block diagram

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Signal Processing Theory}
\label{cha:TheThesis}

@@

\includepicture [1.0] [0] {High-level block diagram of a signal processing chain.} {bd_dsp_overview} {img/draw.io/bd_dsp_overview}

@@

\includepicture [1.0] [0] {Block design of a superhetorodyne receiver \cite[Fig.2.1]{PassosFábio2020AHSo}} {bd_superhet} {img/draw.io/superheterodyne-receiver-block-diagram}

@@

\includepicture [1.0] [0] {Block design of a direct-conversion receiver \cite[Fig.2.3]{PassosFábio2020AHSo}.} {bd_direct_conversion} {img/draw.io/direct-conversion-receiver-block-diagram}

@@

\includepicture [1.0] [0] {Block diagram and signal spectrum of down-conversion.} {bd_down_conversion_spectrum} {img/draw.io/down-conversion-AM-spectrum-and-bd}

@@

\includepicture [1.0] [0] {Signal spectrum, explaining the process of down-conversion.} {down_conversion_spectrum_steps} {img/draw.io/down-conversion-steps-AM-spectrum}

@@

\includepicture [0.95] [0] {
  Frequency spectrum of the sampled baseband signal with its replicas at integer multiples of $f_s$ \cite{ThyagarajanK.S2019ItDS}.\\
  A) $f_s > 2f_{signal}$: $f_s$ is high enough and thus meets the theorem.\\
  B) $f_s = 2f_{signal}$: $f_s$ exactly meets the theorem.\\
  C) $f_s < 2f_{signal}$: $f_s$ is too low and thus creates overlaps of the replicas - aliasing.
} {aliasing_freq_spectrum} {img/draw.io/sampling-aliasing}

@@

\includepicture [1.0] [0] {Allocation of frequencies in an FM channel \cite{FigFmChannelFreqSpectrum}.} {fm_channel_baseband_freqs} {img/draw.io/fm-channel-baseband-freqs}

@@

\includepicture [0.75] [0] {Frequency discriminator block diagram \cite{FigBdFreqDiscriminator}.} {bd_freq_discriminator} {img/draw.io/bd_freq_discriminator}

@@

\includepicture [1.0] [0] {Time-domain signals in envelope detection \cite{RoppelBegleitmaterial}.} {time_domain_envelope_detect} {img/draw.io/envelope-detect-time-domain.png}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Signal Processing Theory}
\label{cha:SignalProcessingTheory}

@@

\includepicture [1.0] {High-level block diagram of a signal processing chain.} {bd_dsp_overview} {img/draw.io/bd_dsp_overview}

@@

\includepicture [1.0] {Block design of a superhetorodyne receiver \cite[Fig.2.1]{PassosFábio2020AHSo}} {bd_superhet} {img/draw.io/superheterodyne-receiver-block-diagram}

@@

\includepicture [1.0] {Block design of a direct-conversion receiver \cite[Fig.2.3]{PassosFábio2020AHSo}.} {bd_direct_conversion} {img/draw.io/direct-conversion-receiver-block-diagram}

@@

\includepicture [1.0] {Block diagram and signal spectrum of down-conversion.} {bd_down_conversion_spectrum} {img/draw.io/down-conversion-AM-spectrum-and-bd}

@@

\includepicture [1.0] {Signal spectrum, explaining the process of down-conversion.} {down_conversion_spectrum_steps} {img/draw.io/down-conversion-steps-AM-spectrum}

@@

\includepicture [0.95] {
  Frequency spectrum of the sampled baseband signal with its replicas at integer multiples of $f_s$ \cite{ThyagarajanK.S2019ItDS}.\\
  A) $f_s > 2f_{signal}$: $f_s$ is high enough and thus meets the theorem.\\
  B) $f_s = 2f_{signal}$: $f_s$ exactly meets the theorem.\\
  C) $f_s < 2f_{signal}$: $f_s$ is too low and thus creates overlaps of the replicas - aliasing.
} {aliasing_freq_spectrum} {img/draw.io/sampling-aliasing}

@@

\includepicture [1.0] {Allocation of frequencies in an FM channel \cite{FigFmChannelFreqSpectrum}.} {fm_channel_baseband_freqs} {img/draw.io/fm-channel-baseband-freqs}

@@

\includepicture [0.75] {Frequency discriminator block diagram \cite{FigBdFreqDiscriminator}.} {bd_freq_discriminator} {img/draw.io/bd_freq_discriminator}

@@

\includepicture [1.0] {Time-domain signals in envelope detection \cite{RoppelBegleitmaterial}.} {time_domain_envelope_detect} {img/draw.io/envelope-detect-time-domain.png}
